\section{wxAda overview}\label{wxadaoverview}

This topic was written by Luke A. Guest, the author of wxAda.

%Classes, functions and macros: \helpref{wxDebugContext}{wxdebugcontext}, \helpref{wxObject}{wxobject}, \helpref{wxLog}{wxlog},
%\rtfsp\helpref{Log functions}{logfunctions}, \helpref{Debug macros}{debugmacros}

\subsection{What is wxAda?}\label{whatiswxada}

wxAda is a set of packages for the Ada95 programming language which wrap up the main components of the wxWidgets library.

\wxheading{Ada}

Ada is a general purpose programming language which was developed for the US DoD back in the 1970's starting with the first standard
Ada83 and then progressing onto Ada95, the next version will be standardised sometime this year Ada05 (or Ada2005).

Ada is a complex language and has support for many features programmers expect, such as function (and operator) overloading,
object-orientation, separate compilation. Ada also incorporates features that some languages have to get around using external libraries,
multithreading, real-time, etc.

Go to \urlref{Ada Home}{http://www.adahome.com}, \urlref{Ada Power}{http://www.adapower.com} and #Ada on Freenode for more information.

\wxheading{wxAda}
\subsection{Why use wxAda?}\label{whyusewxada}

wxAda is the first GUI which can allow programs to be compiled under different platforms using any Ada95 conformant compiler and the
applications will look native on that particular operating system. wxAda doesn't use any compiler specific extensions to implement
the tagged types hierarchy (i.e. class hierarchy).

\subsection{Other Ada GUI's}\label{otheradaguis}

There are a number of different Ada GUI libraries but none are as portable as wxAda nor are they as nice to use from a development point of view.

\wxheading{GtkAda}

This is possibly the most portable GUI available due to the fact that Gtk+ doesn't use the operating system's native controls and thus
can be ported to practically any OS.

\wxheading{Claw}

Windows only binding and commercial.

\wxheading{Gwindows}

Another Windows binding.

\wxheading{AdaBindX}

This is a binding for X11 and requires some rather nasty preprocessing before it can be compiled, just like the C headers.

\subsection{Using wxAda}\label{usingwxada}
\subsection{wxWidgets classes implemented in wxAda}\label{wxwidgetsclassesimplementedinwxada}
